UNIVERSIDAD DE SAN CARLOS DE GUATEMALA
FACULTAD DE INGENIERÍA
ESCUELA DE ESTUDIOS DE POSTGRADO
MAESTRÍA EN INGENIERÍA PARA LA INDUSTRIA CON ESPECIALIZACIÓN EN CIENCIAS DE LA COMPUTACIÓN
CURSO: Fundamentos de Programación y Scripting
ESTUDIANTE: German Omar Chiguichón Sibrian

```{r}
library(dplyr)
library(tidyr)
library(tidyverse)
questions <- read_csv("questions.csv")
answers <- read_csv("answers.csv")
tags <- read_csv("tags.csv")
question_tags <- read.csv("question_tags.csv")
questions
answers
tags
question_tags
```

1. Left-joining questions and tags

```{r}

# 1.1

question_width_tags <- questions %>%
  left_join(question_tags, by = c("id"="question_id"))%>%
  
#1.2
  
  left_join(tags, by =c ("tag_id"="id"))%>%


#1.3
  
  replace_na(list(tag_name="only_r"))

question_width_tags

```

2. Comparing scores across tags

```{r}

#2.1

question_width_tags %>%
  group_by(tag_name) %>%
  
#2.2
  
  summarize(mean_score=mean(score))%>%

#2.3
  
  arrange(desc(mean_score))
```

3. Finding gaps between questions and answers

```{r}

#3.1

#questions
#answers
questions%>%
  inner_join(answers, by =c("id"="question_id"),
  suffix=c("_question", "_answer"))%>%
  
#3.2
    
   mutate(gap = creation_date_answer - creation_date_question)
```

4. Joining question and answer counts

```{r}

#4.1

answer_counts <- answers%>%
  count(question_id)%>%
  arrange(desc(n))

#answer_counts
#questions

#4.2

question_answer_counts <- questions%>%
  left_join(answer_counts, by =c("id"="question_id"))%>%

#4.3
  
  replace_na(list(n=0))

question_answer_counts
```

5. Joining questions, answers, and tags

```{r}

#5.1

#question_tags
#question_answer_counts
#tags
question_tags%>%
  inner_join(question_answer_counts, by =c("question_id"="id"))%>%
  
#5.2
  
  inner_join(tags, by=c("tag_id"="id"))
```

